---
title: "Week 13 Graphs makeover"
author: "Yuting Huang"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      include = TRUE,
                      fig.align = "center",  out.width = "80%")
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)

# Additional packages
library(ggthemes); library(scales)
```


# Graphs makeover
In Week 10 tutorial, we examined some plots in the wild. Now we will try to re-create and improve some of them.

During the process, we will ask ourselves the following questions:

+ How to read in the data?

+ Is the data frame tidy? If not, how should we tidy it up?

+ What are the `geom`s used in the plot? How should we prepare and map the data to these `geom`s?

+ Are there better ways to present and visualize the data?

## Streaming services in the US

```{r}
# Reading in data
df1 <- read.csv("../data/wk13_streamingUS.csv")
head(df1)
```

```{r}
# Preparing the data










# Plotting









```

```{r}
# Improving the visualization
# Preparing the data










# Plotting









```

## Chinese New Year and Thanksgiving

```{r}
# Reading in data
df2 <- read_excel("../data/wk13_cny_thanksgiving.xlsx")
head(df2)
```

```{r}
# Improving the visualization
# Preparing the data










# Plotting









```

## Cereal consumption

```{r}
df3 <- read_excel("../data/wk13_personal_consumption_expenditures.xlsx") %>%
  filter(`Sub-Category` == "Cereals")
head(df3)
```

```{r}
# Preparing the data










# Plotting









```

```{r}
# Improving the visualization
# Preparing the data










# Plotting









```

## Time spent in life

```{r}
df4 <- read.csv("../data/wk13_time-spent-with-relationships-by-age-us.csv") %>%
     rename(age = Year,
         "Alone" = 4,
         "With friends" = 5,
         "With children" = 6,
         "With parents" = 7,
         "With partner" = 8,
         "With coworkers" = 9)
head(df4)
```

```{r}
# Preparing the data










# Plotting









```













